---
title: "CIFAR10 Tuning Results"
author: "Jerry Chee"
date: "7/17/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("cifar_analysis.R")
```

Tuning experiments for ResNet18 on CIFAR10.
Adding mean zero gaussian noise to the gradient.
Extensive experiments conducted on batch size 8192, 4096, 2048.
Plots only shared for 8192, to see the rest of the experimental data see `checkpoint/` folder.
Extensive tuning proved unsuccessful in improving performance on test with added gradient noise.


## Batch Size 8192
Some observations: so far the most promising this is that adding noise prevents the decay in performance as the learning rate increases. 
At learning rate 0.2 and above, adding noise improves the generalization performance.
But, learning rate 0.1 is still best.
Again, I am not sure why the performance decreases with increasing the learning rate.
A starting LR=0.1 is very common for small batch sizes, as I understand.

Smaller noise does better, larger noise does worse.
A decreasing noise does better than a constant noise

```{r, echo=FALSE}
plot_v0.5(cifar.8192.05.dat,
        cifar.8192.1.dat,
        cifar.8192.2.dat,
        cifar.8192.3.dat,
        cifar.8192.4.dat,
        cifar.8192.5.dat,
        title='LR Scaling', legend.names=c(0.05,0.1,0.2,0.3,0.4,0.5), legend.title='LR')

plot_v0(cifar.8192.1.eta005.dat,
        cifar.8192.2.eta005.dat,
        cifar.8192.3.eta005.dat,
        cifar.8192.4.eta005.dat,
        cifar.8192.5.eta005.dat,
        title='LR Scaling with Noise', legend.names=c('0.1+0.005','0.2+0.005','0.3+0.005','0.4+0.005','0.5+0.005'),
        legend.title='LR + Noise')


plot_v1.5(cifar.8192.05.dat,
        cifar.8192.05.eta1e7.dat,
        cifar.8192.05.eta1e6.dat,
        cifar.8192.05.eta1e5.dat,
        cifar.8192.05.eta1e4.dat,
        cifar.8192.05.eta1e3.dat,
        cifar.8192.05.eta005.dat,
        cifar.8192.05.eta01.dat,
        cifar.8192.05.eta1.dat,
        title="LR=0.05 & Decr Noise Scaling", legend.ref="0")

plot_v1.5(cifar.8192.05.dat,
        cifar.8192.05.eta1e7.gam0.dat,
        cifar.8192.05.eta1e6.gam0.dat,
        cifar.8192.05.eta1e5.gam0.dat,
        cifar.8192.05.eta1e4.gam0.dat,
        cifar.8192.05.eta1e3.gam0.dat,
        cifar.8192.05.eta005.gam0.dat,
        cifar.8192.05.eta01.gam0.dat,
        cifar.8192.05.eta1.gam0.dat,
        title="LR=0.05 & Const Noise Scaling", legend.ref="0")

plot_v1.5(cifar.8192.1.dat,
        cifar.8192.1.eta1e7.dat,
        cifar.8192.1.eta1e6.dat,
        cifar.8192.1.eta1e5.dat,
        cifar.8192.1.eta1e4.dat,
        cifar.8192.1.eta1e3.dat,
        cifar.8192.1.eta005.dat,
        cifar.8192.1.eta01.dat,
        cifar.8192.1.eta1.dat,
        title='LR=0.1 & Decr Noise', legend.ref='0')

plot_v1.5(cifar.8192.1.dat,
        cifar.8192.1.eta1e7.gam0.dat,
        cifar.8192.1.eta1e6.gam0.dat,
        cifar.8192.1.eta1e5.gam0.dat,
        cifar.8192.1.eta1e4.gam0.dat,
        cifar.8192.1.eta1e3.gam0.dat,
        cifar.8192.1.eta005.gam0.dat,
        cifar.8192.1.eta01.gam0.dat,
        cifar.8192.1.eta1.gam0.dat,
        title="LR=0.1 & Const Noise Scaling", legend.ref="0")

plot_v1.5(cifar.8192.2.dat,
        cifar.8192.2.eta1e7.dat,
        cifar.8192.2.eta1e6.dat,
        cifar.8192.2.eta1e5.dat,
        cifar.8192.2.eta1e4.dat,
        cifar.8192.2.eta1e3.dat,
        cifar.8192.2.eta005.dat,
        cifar.8192.2.eta01.dat,
        cifar.8192.2.eta1.dat,
        title='LR=0.2 & Decr Noise', legend.ref='0')

plot_v1.5(cifar.8192.2.dat,
        cifar.8192.2.eta1e7.gam0.dat,
        cifar.8192.2.eta1e6.gam0.dat,
        cifar.8192.2.eta1e5.gam0.dat,
        cifar.8192.2.eta1e4.gam0.dat,
        cifar.8192.2.eta1e3.gam0.dat,
        cifar.8192.2.eta005.gam0.dat,
        cifar.8192.2.eta01.gam0.dat,
        cifar.8192.2.eta1.gam0.dat,
        title="LR=0.2 & Const Noise Scaling", legend.ref="0")

plot_v1.5(cifar.8192.3.dat,
        cifar.8192.3.eta1e7.dat,
        cifar.8192.3.eta1e6.dat,
        cifar.8192.3.eta1e5.dat,
        cifar.8192.3.eta1e4.dat,
        cifar.8192.3.eta1e3.dat,
        cifar.8192.3.eta005.dat,
        cifar.8192.3.eta01.dat,
        cifar.8192.3.eta1.dat,
        title='LR=0.3 & Decr Noise', legend.ref='0')

plot_v1.5(cifar.8192.3.dat,
        cifar.8192.3.eta1e7.gam0.dat,
        cifar.8192.3.eta1e6.gam0.dat,
        cifar.8192.3.eta1e5.gam0.dat,
        cifar.8192.3.eta1e4.gam0.dat,
        cifar.8192.3.eta1e3.gam0.dat,
        cifar.8192.3.eta005.gam0.dat,
        cifar.8192.3.eta01.gam0.dat,
        cifar.8192.3.eta1.gam0.dat,
        title="LR=0.3 & Const Noise Scaling", legend.ref="0")

plot_v1.5(cifar.8192.4.dat,
        cifar.8192.4.eta1e7.dat,
        cifar.8192.4.eta1e6.dat,
        cifar.8192.4.eta1e5.dat,
        cifar.8192.4.eta1e4.dat,
        cifar.8192.4.eta1e3.dat,
        cifar.8192.4.eta005.dat,
        cifar.8192.4.eta01.dat,
        cifar.8192.4.eta1.dat,
        title='LR=0.4 & Decr Noise', legend.ref='0')

plot_v1.5(cifar.8192.4.dat,
        cifar.8192.4.eta1e7.gam0.dat,
        cifar.8192.4.eta1e6.gam0.dat,
        cifar.8192.4.eta1e5.gam0.dat,
        cifar.8192.4.eta1e4.gam0.dat,
        cifar.8192.4.eta1e3.gam0.dat,
        cifar.8192.4.eta005.gam0.dat,
        cifar.8192.4.eta01.gam0.dat,
        cifar.8192.4.eta1.gam0.dat,
        title="LR=0.4 & Const Noise Scaling", legend.ref="0")


# plot_v1(cifar.8192.3.dat,
#         cifar.8192.3.eta005.dat,
#         cifar.8192.3.eta01.dat,
#         cifar.8192.3.eta1.dat,
#         title="LR=0.3 & Decr Noise Scaling", legend.ref="0")
# plot_v1(cifar.8192.2.dat,
#         cifar.8192.2.eta005.gam0.dat,
#         cifar.8192.2.eta01.gam0.dat,
#         cifar.8192.2.eta1.gam0.dat,
#         title="LR=0.2 & Const Noise Scaling", legend.ref="0")
# 
# plot_v1(cifar.8192.3.dat,
#         cifar.8192.3.eta005.gam0.dat,
#         cifar.8192.3.eta01.gam0.dat,
#         cifar.8192.3.eta1.gam0.dat,
#         title="LR=0.3 & Const Noise Scaling", legend.ref="0")

# plot_v1(cifar.8192.4.dat,
#         cifar.8192.4.eta005.dat,
#         cifar.8192.4.eta01.dat,
#         cifar.8192.4.eta1.dat,
#         title="LR=0.4 & Decr Noise Scaling", legend.ref="0")

plot_v1(cifar.8192.5.dat,
       cifar.8192.5.eta005.dat,
       cifar.8192.5.eta01.dat,
       cifar.8192.5.eta1.dat,
       title="LR=0.5 & Decr Noise Scaling", legend.ref="0")

# # plot_v1(cifar.8192.4.dat,
# #         cifar.8192.4.eta005.gam0.dat,
# #         cifar.8192.4.eta01.gam0.dat,
# #         cifar.8192.4.eta1.gam0.dat,
# #         title="LR=0.4 & Const Noise Scaling", legend.ref="0")
# # 
# plot_v1(cifar.8192.5.dat,
#         cifar.8192.5.eta005.gam0.dat,
#         cifar.8192.5.eta01.gam0.dat,
#         cifar.8192.5.eta1.gam0.dat,
#         title="LR=0.5 & Const Noise Scaling", legend.ref="0")
```


```{r, echo=FALSE, eval=FALSE}
## Batch Size 4096
#Some observations: so far the most promising this is that adding noise prevents the decay in performance as the learning rate increases. 
#Again, I am not sure why the performance decreases with increasing the learning rate.
#A starting LR=0.1 is very common for small batch sizes, as I understand.
plot_v0.5(cifar.4096.05.dat,
        cifar.4096.1.dat,
        cifar.4096.2.dat,
        cifar.4096.3.dat,
        cifar.4096.4.dat,
        cifar.4096.5.dat,
        title='LR Scaling', legend.names=c(0.05,0.1,0.2,0.3,0.4,0.5), legend.title='LR')

plot_v0(cifar.4096.1.eta005.dat,
        cifar.4096.2.eta005.dat,
        cifar.4096.3.eta005.dat,
        cifar.4096.4.eta005.dat,
        cifar.4096.5.eta005.dat,
        title='LR Scaling with Noise', legend.names=c('0.1+0.005','0.2+0.005','0.3+0.005','0.4+0.005','0.5+0.005'),
        legend.title='LR + Noise')


plot_v1.5(cifar.4096.05.dat,
        cifar.4096.05.eta1e7.dat,
        cifar.4096.05.eta1e6.dat,
        cifar.4096.05.eta1e5.dat,
        cifar.4096.05.eta1e4.dat,
        cifar.4096.05.eta1e3.dat,
        cifar.4096.05.eta005.dat,
        cifar.4096.05.eta01.dat,
        cifar.4096.05.eta1.dat,
        title="LR=0.05 & Decr Noise Scaling", legend.ref="0")

plot_v1.5(cifar.4096.05.dat,
        cifar.4096.05.eta1e7.gam0.dat,
        cifar.4096.05.eta1e6.gam0.dat,
        cifar.4096.05.eta1e5.gam0.dat,
        cifar.4096.05.eta1e4.gam0.dat,
        cifar.4096.05.eta1e3.gam0.dat,
        cifar.4096.05.eta005.gam0.dat,
        cifar.4096.05.eta01.gam0.dat,
        cifar.4096.05.eta1.gam0.dat,
        title="LR=0.05 & Const Noise Scaling", legend.ref="0")

plot_v1.5(cifar.4096.1.dat,
        cifar.4096.1.eta1e7.dat,
        cifar.4096.1.eta1e6.dat,
        cifar.4096.1.eta1e5.dat,
        cifar.4096.1.eta1e4.dat,
        cifar.4096.1.eta1e3.dat,
        cifar.4096.1.eta005.dat,
        cifar.4096.1.eta01.dat,
        cifar.4096.1.eta1.dat,
        title='LR=0.1 & Decr Noise', legend.ref='0')

plot_v1.5(cifar.4096.1.dat,
        cifar.4096.1.eta1e7.gam0.dat,
        cifar.4096.1.eta1e6.gam0.dat,
        cifar.4096.1.eta1e5.gam0.dat,
        cifar.4096.1.eta1e4.gam0.dat,
        cifar.4096.1.eta1e3.gam0.dat,
        cifar.4096.1.eta005.gam0.dat,
        cifar.4096.1.eta01.gam0.dat,
        cifar.4096.1.eta1.gam0.dat,
        title="LR=0.1 & Const Noise Scaling", legend.ref="0")

plot_v1.5(cifar.4096.2.dat,
        cifar.4096.2.eta1e7.dat,
        cifar.4096.2.eta1e6.dat,
        cifar.4096.2.eta1e5.dat,
        cifar.4096.2.eta1e4.dat,
        cifar.4096.2.eta1e3.dat,
        cifar.4096.2.eta005.dat,
        cifar.4096.2.eta01.dat,
        cifar.4096.2.eta1.dat,
        title='LR=0.2 & Decr Noise', legend.ref='0')

plot_v1.5(cifar.4096.2.dat,
        cifar.4096.2.eta1e7.gam0.dat,
        cifar.4096.2.eta1e6.gam0.dat,
        cifar.4096.2.eta1e5.gam0.dat,
        cifar.4096.2.eta1e4.gam0.dat,
        cifar.4096.2.eta1e3.gam0.dat,
        cifar.4096.2.eta005.gam0.dat,
        cifar.4096.2.eta01.gam0.dat,
        cifar.4096.2.eta1.gam0.dat,
        title="LR=0.2 & Const Noise Scaling", legend.ref="0")

plot_v1.5(cifar.4096.3.dat,
        cifar.4096.3.eta1e7.dat,
        cifar.4096.3.eta1e6.dat,
        cifar.4096.3.eta1e5.dat,
        cifar.4096.3.eta1e4.dat,
        cifar.4096.3.eta1e3.dat,
        cifar.4096.3.eta005.dat,
        cifar.4096.3.eta01.dat,
        cifar.4096.3.eta1.dat,
        title='LR=0.3 & Decr Noise', legend.ref='0')

plot_v1.5(cifar.4096.3.dat,
        cifar.4096.3.eta1e7.gam0.dat,
        cifar.4096.3.eta1e6.gam0.dat,
        cifar.4096.3.eta1e5.gam0.dat,
        cifar.4096.3.eta1e4.gam0.dat,
        cifar.4096.3.eta1e3.gam0.dat,
        cifar.4096.3.eta005.gam0.dat,
        cifar.4096.3.eta01.gam0.dat,
        cifar.4096.3.eta1.gam0.dat,
        title="LR=0.3 & Const Noise Scaling", legend.ref="0")

plot_v1.5(cifar.4096.4.dat,
        cifar.4096.4.eta1e7.dat,
        cifar.4096.4.eta1e6.dat,
        cifar.4096.4.eta1e5.dat,
        cifar.4096.4.eta1e4.dat,
        cifar.4096.4.eta1e3.dat,
        cifar.4096.4.eta005.dat,
        cifar.4096.4.eta01.dat,
        cifar.4096.4.eta1.dat,
        title='LR=0.4 & Decr Noise', legend.ref='0')

plot_v1.5(cifar.4096.4.dat,
        cifar.4096.4.eta1e7.gam0.dat,
        cifar.4096.4.eta1e6.gam0.dat,
        cifar.4096.4.eta1e5.gam0.dat,
        cifar.4096.4.eta1e4.gam0.dat,
        cifar.4096.4.eta1e3.gam0.dat,
        cifar.4096.4.eta005.gam0.dat,
        cifar.4096.4.eta01.gam0.dat,
        cifar.4096.4.eta1.gam0.dat,
        title="LR=0.4 & Const Noise Scaling", legend.ref="0")


# plot_v1(cifar.4096.3.dat,
#         cifar.4096.3.eta005.dat,
#         cifar.4096.3.eta01.dat,
#         cifar.4096.3.eta1.dat,
#         title="LR=0.3 & Decr Noise Scaling", legend.ref="0")
# plot_v1(cifar.4096.2.dat,
#         cifar.4096.2.eta005.gam0.dat,
#         cifar.4096.2.eta01.gam0.dat,
#         cifar.4096.2.eta1.gam0.dat,
#         title="LR=0.2 & Const Noise Scaling", legend.ref="0")
# 
# plot_v1(cifar.4096.3.dat,
#         cifar.4096.3.eta005.gam0.dat,
#         cifar.4096.3.eta01.gam0.dat,
#         cifar.4096.3.eta1.gam0.dat,
#         title="LR=0.3 & Const Noise Scaling", legend.ref="0")

# plot_v1(cifar.4096.4.dat,
#         cifar.4096.4.eta005.dat,
#         cifar.4096.4.eta01.dat,
#         cifar.4096.4.eta1.dat,
#         title="LR=0.4 & Decr Noise Scaling", legend.ref="0")

plot_v1(cifar.4096.5.dat,
       cifar.4096.5.eta005.dat,
       cifar.4096.5.eta01.dat,
       cifar.4096.5.eta1.dat,
       title="LR=0.5 & Decr Noise Scaling", legend.ref="0")

# # plot_v1(cifar.4096.4.dat,
# #         cifar.4096.4.eta005.gam0.dat,
# #         cifar.4096.4.eta01.gam0.dat,
# #         cifar.4096.4.eta1.gam0.dat,
# #         title="LR=0.4 & Const Noise Scaling", legend.ref="0")
# # 
# plot_v1(cifar.4096.5.dat,
#         cifar.4096.5.eta005.gam0.dat,
#         cifar.4096.5.eta01.gam0.dat,
#         cifar.4096.5.eta1.gam0.dat,
#         title="LR=0.5 & Const Noise Scaling", legend.ref="0")
```



```{r, echo=FALSE, eval=FALSE}
plot_v0(cifar.4096.1.dat,
        cifar.4096.2.dat,
        cifar.4096.3.dat,
        cifar.4096.4.dat,
        cifar.4096.5.dat,
        title='LR Scaling', legend.names=c(0.1,0.2,0.3,0.4,0.5), legend.title='LR')

plot_v0(cifar.4096.1.eta005.dat,
        cifar.4096.2.eta005.dat,
        cifar.4096.3.eta005.dat,
        cifar.4096.4.eta005.dat,
        cifar.4096.5.eta005.dat,
        title='LR Scaling with Noise', legend.names=c('0.1+0.005','0.2+0.005','0.3+0.005','0.4+0.005','0.5+0.005'), 
        legend.title='LR + Noise')


par(mfrow=c(1,2))
plot_v1(cifar.4096.1.dat,
        cifar.4096.05.eta005.dat,
        cifar.4096.05.eta01.dat,
        cifar.4096.05.eta1.dat,
        title="LR=0.05 & Decr Noise Scaling", legend.ref="0, LR=0.1")

plot_v1(cifar.4096.1.dat,
        cifar.4096.1.eta005.dat,
        cifar.4096.1.eta01.dat,
        cifar.4096.1.eta1.dat,
        title='LR=0.1 & Decr Noise', legend.ref='0')

plot_v1(cifar.4096.1.dat,
        cifar.4096.05.eta005.gam0.dat,
        cifar.4096.05.eta01.gam0.dat,
        cifar.4096.05.eta1.gam0.dat,
        title="LR=0.05 & Const Noise Scaling", legend.ref="0, LR=0.1")

plot_v1(cifar.4096.1.dat,
        cifar.4096.1.eta005.gam0.dat,
        cifar.4096.1.eta01.gam0.dat,
        cifar.4096.1.eta1.gam0.dat,
        title="LR=0.1 & Const Noise Scaling", legend.ref="0")

plot_v1(cifar.4096.2.dat,
        cifar.4096.2.eta005.dat,
        cifar.4096.2.eta01.dat,
        cifar.4096.2.eta1.dat,
        title="LR=0.2 & Decr Noise Scaling", legend.ref="0")

plot_v1(cifar.4096.3.dat,
        cifar.4096.3.eta005.dat,
        cifar.4096.3.eta01.dat,
        cifar.4096.3.eta1.dat,
        title="LR=0.3 & Decr Noise Scaling", legend.ref="0")

plot_v1(cifar.4096.2.dat,
        cifar.4096.2.eta005.gam0.dat,
        cifar.4096.2.eta01.gam0.dat,
        cifar.4096.2.eta1.gam0.dat,
        title="LR=0.2 & Const Noise Scaling", legend.ref="0")

plot_v1(cifar.4096.3.dat,
        cifar.4096.3.eta005.gam0.dat,
        cifar.4096.3.eta01.gam0.dat,
        cifar.4096.3.eta1.gam0.dat,
        title="LR=0.3 & Const Noise Scaling", legend.ref="0")

plot_v1(cifar.4096.4.dat,
        cifar.4096.4.eta005.dat,
        cifar.4096.4.eta01.dat,
        cifar.4096.4.eta1.dat,
        title="LR=0.4 & Decr Noise Scaling", legend.ref="0")

plot_v1(cifar.4096.5.dat,
        cifar.4096.5.eta005.dat,
        cifar.4096.5.eta01.dat,
        cifar.4096.5.eta1.dat,
        title="LR=0.5 & Decr Noise Scaling", legend.ref="0")

# plot_v1(cifar.4096.4.dat,
#         cifar.4096.4.eta005.gam0.dat,
#         cifar.4096.4.eta01.gam0.dat,
#         cifar.4096.4.eta1.gam0.dat,
#         title="LR=0.4 & Const Noise Scaling", legend.ref="0")
# 
# plot_v1(cifar.4096.5.dat,
#         cifar.4096.5.eta005.gam0.dat,
#         cifar.4096.5.eta01.gam0.dat,
#         cifar.4096.5.eta1.gam0.dat,
#         title="LR=0.5 & Const Noise Scaling", legend.ref="0")
```


```{r, echo=FALSE, eval=FALSE}
## Batch Size 2048
#Some observations: so far the most promising this is that adding noise prevents the decay in performance as the learning rate increases. 
#Again, I am not sure why the performance decreases with increasing the learning rate.
#A starting LR=0.1 is very common for small batch sizes, as I understand.

plot_v0(cifar.2048.1.dat,
        cifar.2048.2.dat,
        cifar.2048.3.dat,
        cifar.2048.4.dat,
        cifar.2048.5.dat,
        title='LR Scaling', legend.names=c(0.1,0.2,0.3,0.4,0.5), legend.title='LR')

# plot_v0(cifar.2048.1.eta005.dat,
#         cifar.2048.2.eta005.dat,
#         cifar.2048.3.eta005.dat,
#         cifar.2048.4.eta005.dat,
#         cifar.2048.5.eta005.dat,
#         title='LR Scaling with Noise', legend.names=c('0.1+0.005','0.2+0.005','0.3+0.005','0.4+0.005','0.5+0.005'), 
#         legend.title='LR + Noise')


par(mfrow=c(1,2))
plot_v1(cifar.2048.1.dat,
        cifar.2048.05.eta005.dat,
        cifar.2048.05.eta01.dat,
        cifar.2048.05.eta1.dat,
        title="LR=0.05 & Decr Noise Scaling", legend.ref="0, LR=0.1")

plot_v1(cifar.2048.1.dat,
        cifar.2048.1.eta005.dat,
        cifar.2048.1.eta01.dat,
        cifar.2048.1.eta1.dat,
        title='LR=0.1 & Decr Noise', legend.ref='0')

plot_v1(cifar.2048.1.dat,
        cifar.2048.05.eta005.gam0.dat,
        cifar.2048.05.eta01.gam0.dat,
        cifar.2048.05.eta1.gam0.dat,
        title="LR=0.05 & Const Noise Scaling", legend.ref="0, LR=0.1")

plot_v1(cifar.2048.1.dat,
        cifar.2048.1.eta005.gam0.dat,
        cifar.2048.1.eta01.gam0.dat,
        cifar.2048.1.eta1.gam0.dat,
        title="LR=0.1 & Const Noise Scaling", legend.ref="0")

plot_v1(cifar.2048.2.dat,
        cifar.2048.2.eta005.dat,
        cifar.2048.2.eta01.dat,
        cifar.2048.2.eta1.dat,
        title="LR=0.2 & Decr Noise Scaling", legend.ref="0")

plot_v1(cifar.2048.3.dat,
        cifar.2048.3.eta005.dat,
        cifar.2048.3.eta01.dat,
        cifar.2048.3.eta1.dat,
        title="LR=0.3 & Decr Noise Scaling", legend.ref="0")

plot_v1(cifar.2048.2.dat,
        cifar.2048.2.eta005.gam0.dat,
        cifar.2048.2.eta01.gam0.dat,
        cifar.2048.2.eta1.gam0.dat,
        title="LR=0.2 & Const Noise Scaling", legend.ref="0")

# plot_v1(cifar.2048.3.dat,
#         cifar.2048.3.eta005.gam0.dat,
#         cifar.2048.3.eta01.gam0.dat,
#         cifar.2048.3.eta1.gam0.dat,
#         title="LR=0.3 & Const Noise Scaling", legend.ref="0")
# 
# plot_v1(cifar.2048.4.dat,
#         cifar.2048.4.eta005.dat,
#         cifar.2048.4.eta01.dat,
#         cifar.2048.4.eta1.dat,
#         title="LR=0.4 & Decr Noise Scaling", legend.ref="0")
# 
# plot_v1(cifar.2048.5.dat,
#         cifar.2048.5.eta005.dat,
#         cifar.2048.5.eta01.dat,
#         cifar.2048.5.eta1.dat,
#         title="LR=0.5 & Decr Noise Scaling", legend.ref="0")
# 
# # plot_v1(cifar.2048.4.dat,
#         cifar.2048.4.eta005.gam0.dat,
#         cifar.2048.4.eta01.gam0.dat,
#         cifar.2048.4.eta1.gam0.dat,
#         title="LR=0.4 & Const Noise Scaling", legend.ref="0")
# 
# plot_v1(cifar.2048.5.dat,
#         cifar.2048.5.eta005.gam0.dat,
#         cifar.2048.5.eta01.gam0.dat,
#         cifar.2048.5.eta1.gam0.dat,
#         title="LR=0.5 & Const Noise Scaling", legend.ref="0")
```